---
title: "Project 1 Analysis"
output: html_notebook
---

Import libaries and data
```{r}
library("readxl")
data = read_excel("data.xlsx")
```

Testing that "Hard Punch" is reliable 70% of the time.
Null hypothesis is that hard_punch_success <= 70%
```{r}
t.test(data$hard_punch_success, alternative = "greater", mu = 7)
```

Testing that "Precision Spin" is reliable 70% of the time.
Null hypothesis is that spin_success <= 70%
```{r}
t.test(data$spin_success, alternative = "greater", mu = 7)
```

Testing that we don't have false activations of "Hard Punch" when performing "Precision Spin". Testing that we don't have false activations of "Precision Spin" when performing "Hard Punch".

Two sample T-test
```{r}
t.test(x=data$punch_activation_when_expect_spin, y= data$spin_activation_when_expect_punch, paired=TRUE)
```


Testing that we don't have false activations when walking.

Two-sample T-test
```{r}
t.test(x=data$punch_activations_during_walk, y= data$spin_activations_during_walk, paired=TRUE)

```

Testing that we don't have false activations when drawing.
Two sample T-test
```{r}
t.test(x=data$punch_activations_during_draw, y= data$spin_activations_during_draw, paired=TRUE)
```

Boxplot section
```{r}
boxplot(data$hard_punch_success, main="Hard Punch Reliability",
   xlab = "Hard Punch", ylab="Number successes per 10")
```

```{r}
boxplot(data$spin_success, main="Precision Spin Reliability",
   xlab = "Precision Spin", ylab="Number successes per 10")
```

```{r}
Punch <- data$punch_activation_when_expect_spin
Spin <- data$spin_activation_when_expect_punch
walk_data <- data.frame(Spin, Punch)
boxplot(walk_data, main="Cross-Gesture Robustness",
   ylab="Number per trial")
```


```{r}
Punch <- data$punch_activations_during_walk
Spin <- data$spin_activations_during_walk
walk_data <- data.frame(Spin, Punch)
boxplot(walk_data, main="Accidental Activation during Everyday Activities",
   ylab="Number per trial")
```


```{r}
Punch <- data$punch_activations_during_draw
Spin <- data$spin_activations_during_draw
walk_data <- data.frame(Spin, Punch)
boxplot(walk_data, main="Accidental Activation during Phone Use",
   ylab="Number per trial")
```
