---
title: "Project 1 Analysis"
output: html_notebook
---

Import libaries and data
```{r}
library("readxl")
data = read_excel("data.xlsx")
```

Testing that "Hard Punch" is reliable 70% of the time.
Null hypothesis is that hard_punch_success <= 70%
```{r}
t.test(data$hard_punch_success, alternative = "greater", mu = 7)
```

Testing that "Precision Spin" is reliable 70% of the time.
Null hypothesis is that spin_success <= 70%
```{r}
t.test(data$spin_success, alternative = "greater", mu = 7)
```

Testing that we don't have false activations of "Hard Punch" when performing "Precision Spin".
Null hypothesis is that number of activations is greater than 1.
```{r}
t.test(data$punch_activation_when_expect_spin, alternative = "less", mu = 1)
```


Testing that we don't have false activations of "Precision Spin" when performing "Hard Punch".
Null hypothesis is that number of activations is greater than 1.
```{r}
t.test(data$spin_activation_when_expect_punch, alternative = "less", mu = 1)
```

Testing that we don't have false activations when walking.
Null hypothesis is that number of activations is greater than 1.
```{r}
t.test(data$activations_during_walk, alternative = "less", mu = 1)
```

Testing that we don't have false activations when drawing.
Null hypothesis is that number of activations is greater than 1.
```{r}
t.test(data$activations_during_draw, alternative = "less", mu = 1)
```
